ps4_models

### 2020-10-28 bi-model.Rmd
modelling attempts

```{r}
library(haven)
library(tidyverse)
library(nnet)
```

@@

```{r}
raw_data <- read_dta("inputs/data/ns20200625/ns20200625.dta")
# Add the labels
raw_data <- labelled::to_factor(raw_data)
```

```{r}
reduced_data <- 
  raw_data %>% 
  select(vote_intention,
         vote_2020,
         state,
         race_ethnicity,
         age,
         gender,
         household_income
  )
reduced_data <- reduced_data[complete.cases(reduced_data), ]

@@

levels(reduced_data$race_ethnicity )

>>>>

```{r}
library(haven)
library(tidyverse)
library(nnet)
library(Metrics)

@@

```{r}
raw_data <- read_dta("inputs/data/ns20200625/ns20200625.dta")
# Add the labels
raw_data <- labelled::to_factor(raw_data)
```
```{r}
colnames(raw_data)
```

```{r}
reduced_data <- 
  raw_data %>% 
  select(vote_intention,
         vote_2020,
         state,
         race_ethnicity,
         age,
         gender,
         household_income,
         education
  )
reduced_data <- reduced_data[complete.cases(reduced_data), ]

@@

total_rows <- nrow(reduced_data)

```
```{r}
shuffle_indices <- sample(total_rows)
data <- reduced_data[shuffle_indices,]
boundary <- as.integer(total_rows*0.9)

training <- data[0:boundary,]
model <- nnet::multinom(vote_2020 ~ state + race_ethnicity + gender + 
                          household_income + education, data = training)
```

```{r}
testing <- data[boundary:total_rows,]

probability <- predict(model, newdata = training, "probs")
column_index <- max.col(probability, tie="random")

testing_predictions <- colnames(probability)[column_index]
testing_ground_truth <- training %>% pull(vote_2020)
accuracy(testing_ground_truth, testing_predictions)
